\documentclass[12pt]{article}
\usepackage{zed-csp}%from

\begin{document}

\title{MAKERERE UNIVERSITY\\COLLEGE OF COMPUTING AND INFORMATION SCIENCES\\DEPARTMENT OF COMPUTER SCIENCES.\\A TOPIC ABOUT GOOGLE PRODUCTS PARTICULARLY CLOUD STORAGE}
\author{AHMED SERWANDA\\
       REG No 16/U/20179/EVE and\\ STD No 216021713}
\maketitle
\newpage
\begin{section}
Google is an American IT company which has a number of products its currently providing to the world.Amongst some them are gmail,google app engine,android studio,beacons,google API etc.\\But for this article is we are particularly intrested in one of google products called cloud storage(cloud computing\\
Cloud Computing is a term that encompasses a wide range of use cases and implementation models. In
essence, a computing ‘cloud’ is a large shared pool of computing resources including data storage. When
someone needs additional computing power, they are simply able to check this out of the pool without
much (often any) manual effort on the part of the IT team, which reduces costs and significantly shortens
the time needed to start using new computing resources. Most of these ‘clouds’ are run on the public
Internet by well-known companies like Amazon and Google.where similar economies of scale begin to
apply.\cite{neil}
Case studies provide detailed tools for analysis of cloud storage devices using popular cloud storage services
Includes coverage of the legal implications of cloud storage forensic investigations.\cite{darren}
While nearly all have premium offerings that provide more space, the free cloud storage offered is usually more than enough for most people.

Better yet, many of these free cloud storage providers give you even more free space for referring friends or performing other tasks.\cite{stacy}
\end{section}

\begin{thebibliography}{9}
 \bibitem{neil}  Neil Beagrie, Andrew Charlesworth, and Paul Miller. \textit{How Cloud Storage can address the needs of public archives in the UK}
 
\bibitem{darren} Darren Quick, Ben Martini, Raymond Choo. \textit{"Cloud Storage Forensics"} 
Internet: https://www.kobo.com/gb/en/ebook/cloud-storage-forensics 
\bibitem{stacy} Stacy Fisher. \textit{"The Best Cloud Storage Services for Backup in 2018"} 
Internet:https://www.thebalance.com/free-cloud-storage-1356638.


 \end{thebibliography} 

\end{document}